A Flexible Generator of Constrained Global Optimization Test Problems

### 2018-07-19 2018/LeGo/LeGo.tex
After review

\pdfmapfile{+txfonts.map}

%%%%%ƒŒ¡¿¬»À ƒÀﬂ –”—— Œ√Œ “≈ —“¿
\usepackage[utf8x]{inputenc}
\usepackage[english,russian]{babel}
\usepackage{cmap}
%%%%%

@@

\Russian
???????? ????????? ???????? ????? ?????????????????? ??????????? ? ????????????? ???????? ??????????, ?.?. ??????? ???????? ??????????????? ????? ????? ???????? ??????????? ???????? ????????? ?????? ??????????????? ??????????. 
????????? ?????????? ?????????, ??? ???????, ?????? ??? ???????????. ????????, ????? ????????? ????????? ????? ??? ??????????? ???? ?????????? ?????????? (???????? ???????? ? \cite{Grishagin1997,Grishagin2015}). Another generator (\textit{GKLS generator}) for the functions of arbitrary dimensionality has been proposed in \cite{Gaviano2003}.  GKLS-generator ??? ??????? ???????? ??? ???????????? ????????? ??????? ?????????? ??????????? \cite{Paulavicius2014,Sergeyev2015,Grishagin2018}.

?? ?????? ?????????? GKLS ??? ????????? ?????? ? ?????????? ???????? ????? ? ????????????? (Emmental-type GKLS-based test problems, \cite{Sergeyev2017}. ? ?????? ?????????? ??????? ???????? ???????? ???????????????? GKLS-???????, ????????????? ???????? exterior of a ball ? ????????? ???????? ? ?????????. ????????????? ???? ??????? ??????? ?/??? ??????????? ??????????, ??? ???????? ??????????? ??????? ??????????.

@@

\Russian

@@

Note that since the search of the point $y^*$ is performed in each coordinate separately, the 
computation costs would increase linearly with increasing the dimensionality of the problem.
\Russian 
??? ???? ??????????? ?? ????? ??? $2N\left\|b-a\right\|/h$ ?????????? ???????? ??????? ??????? ???????.

@@

\Russian
???????, ??? volume fraction of the feasible domain ??? ?????? ???? ????? ????? ????? $\Delta = 0.5$, ? ??? ????????? ?????? ????? ?? ????? ??? $\Delta = 0.5$ (?.?. ??? ????????? ?????? ??????? ???? ????? ?????????? ??????? ????? ??????????).

\begin{figure}[ht]
  \centering
  \begin{tabular}[b]{cc}
    \includegraphics[width=.44\linewidth]{1.png} & \includegraphics[width=.44\linewidth]{2.png}\\
    \small (a) & \small (b) \\
    \includegraphics[width=.44\linewidth]{3.png} & \includegraphics[width=.44\linewidth]{4.png}\\
    \small (c) & \small (d) 
  \end{tabular}
  \caption{The test problems generated by GCGen}
	\label{fig:VAG}
\end{figure}

Figures~\ref{fig:VAG} (a,b,c,d) also shows the points of 425, 381, 289 and 188 trials, 
correspondingly, performed by the \textit{index method} for solving constrained global 
optimization problems until the required accuracy $\epsilon=10^{-2}$ was achieved. The 
conditional optimizer is shown as a red point and the best estimation of the optimizer is shown 
as a blue point.

The index method has been developed in 
\cite{Strongin2000,Sergeyev2001,Barkalov2002}. The approach is based on a separate 
accounting for each constraint of the problem and is not related to the use of the penalty 
functions. According to the rules of index method, every iteration includes a sequential 
checking of fulfillment of the problem constraints at this point. The first occurrence of violation 
of any constraint terminates the trial and initiates the transition to the next iteration. This allows: 
(i) accounting for the information on each constraint separately and (ii) solving the problems, in 
which the function values may be undefined out of the feasible domain. 
%It should be noted, that the index method can be efficiently parallelized for accelerators 
%\cite{Barkalov2015,Barkalov2016}.

>>>>

%\pdfmapfile{+txfonts.map}

%%%%%ДОБАВИЛ ДЛЯ РУССКОГО ТЕКСТА
%\usepackage[utf8x]{inputenc}
%\usepackage[english,russian]{babel}
%\usepackage{cmap}
%%%%%

@@

%\Russian
%Проблема построения генераторов многоэкстремальных тестовых задач с невыпуклыми ограничениями является актуальной, т.к. стандартный подход к исследованию и сравнению алгоритмов многоэкстремальной оптимизации основан на решении серии тестовых задач.
%Известные генераторы порождают, как правило, задачи без ограничений. Например, способ построения двумерных тестовых функций был предложен Гришагиным (описание доступно в \cite{Grishagin1997,Grishagin2015}). Another generator (\textit{GKLS generator}) for the functions of arbitrary dimensionality has been proposed in \cite{Gaviano2003}.  GKLS-generator был успешно применен при исследовании некоторых методов глобальной оптимизации \cite{Paulavicius2014,Sergeyev2015,Grishagin2018}.

%На основе генератора GKLS был предложен подход к построению задач с ограничениями (Emmental-type GKLS-based test problems, \cite{Sergeyev2017}. В данном генераторе в качестве целевой функции используется модифицированная GKLS-функция, ограничениями являются exterior of a ball с заданными центрами и радиусами. Использование иных целевых функций и/или ограничений недоступно, что является недостатком данного генератора.

The problem of developing the generators of the multiextremal test problems with non-convex 
constraints is a relevant one since standard approach to investigating and comparing the 
global optimization algorithms is based on solving a series of test problems.
Well known generators generate the problems without constraints as a rule. For example, a 
method for constructing two-dimensional test functions has been proposed by Grishagin (its 
description can be found in \cite{Grishagin1997,Grishagin2015}). Another generator 
(\textit{GKLS generator}) for the functions of arbitrary dimensionality has been proposed in 
\cite{Gaviano2003}.  GKLS generator has been successfully applied in the investigation of some global 
optimization methods \cite{Paulavicius2014,Sergeyev2015,Grishagin2018}.
Based on the GKLS generator, an approach to constructing the constrained problems has been 
proposed (Emmental-type GKLS-based test problems \cite{Sergeyev2017}). In this generator, 
the modified GKLS-function was used as the objective function, the constraints were the 
exterior of the balls with given centers and radii. The use of other objective functions and/or 
constraints was not allowed that was a disadvantage of this generator.

@@

@@

Note that since the search of the point $y^*$ is performed in each coordinate separately, the 
computation costs would increase linearly with increasing the dimensionality of the problem.
%\Russian 
At that, no more than $2N\left\|b-a\right\|/h$ computations of the objective function and 
constraints values will be required.

@@

%\Russian
Note that the volume fraction of the feasible domain for the first three problems will be equal to 
$\Delta = 0.5$, and will be no more than $\Delta = 0.5$ for the last problem (because the 
volume of feasible domain can decrease when generating the problems with controlled number 
of active constraints).

\begin{figure}[ht]
  \centering
  \begin{tabular}[b]{cc}
    \includegraphics[width=.42\linewidth]{1.png} & \includegraphics[width=.42\linewidth]{2.png}\\
    \small (a) & \small (b) \\
    \includegraphics[width=.42\linewidth]{3.png} & \includegraphics[width=.42\linewidth]{4.png}\\
    \small (c) & \small (d) 
  \end{tabular}
  \caption{The test problems generated by GCGen}
	\label{fig:VAG}
\end{figure}

Figures~\ref{fig:VAG} (a,b,c,d) also shows the points of 425, 381, 289 and 188 trials, 
correspondingly, performed by the \textit{index method} for solving constrained global 
optimization problems until the required accuracy $\epsilon=10^{-2}$ was achieved. The 
conditional optimizer is shown as a red point and the best estimation of the optimizer is shown 
as a blue point.
The index method has been developed in 
\cite{Strongin2000,Sergeyev2001,Barkalov2002}. The approach is based on a separate 
accounting for each constraint of the problem and is not related to the use of the penalty 
functions.

%\Russian
The index objective function utilized in the method essentially differs from the classical penalty one 
 since the computing of the initial objective function value outside the feasible 
domain is not required in the index method. Moreover, it is not required to compute the values 
of all constraints outside the feasible domain as well but until the occurrence of the first 
violated one only whereas in the classical penalty problems all constraints along with the 
objective function are computed at every point.
This allows the index method: 
(i) accounting for the information on each constraint separately and (ii) solving the problems, in 
which the function values may be undefined out of the feasible domain. 
%It should be noted, that the index method can be efficiently parallelized for accelerators 
%\cite{Barkalov2015,Barkalov2016}.
